---
title: "Connecting to API"
author: "Caroline Cavallari & Jose de Los Heros"
date: "10/30/2021"
output: html_document
output: ioslides_presentation
keep_md: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---

## Our work for today:
###- We will discuss the definition of APIs
###- We will talk about how API workd and why are they important
###- We will teach you how to do a cool API!
-
      
      
# Defining APIs - What are they and why are they so cool?
APIs are application programming interfaces that allowe programs to talk to each other based on a specific communication.
APIs are organized as MAPs with different level of information, for example, blablabla
You need to know how to ask the questions in order to get the answers that you want!

httr: for making requests
jsonlite and xml2: they will help you parse the response
dplyr



httr request functions are:
HEAD(): getting the body  of the meta data without the data itself in order to understand the variablesyou are dealing with
GET(): getting information from the web into your scripts
POST(): write back to a data store of some kind
PATCH(): 
PUT()
DELETE()

    
    
Now that we know what an API is, we will install some packages that will help us to wok with them:
```{r setup, include=FALSE}

## Load and install the packages that we'll be using today
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, httr, lubridate, janitor, jsonlite, magrittr)
#Now, we upload these packages:
library(tidyverse)
library(httr)
library(lubridate)
library(janitor)
library(jsonlite)
library(magrittr)

```



```{r setup, include=FALSE}


```



```{r setup, include=FALSE}


```


